Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-08-13 analysis/paper/paper.Rmd
minor changes to introduction
try to get rid of white space around map

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```

@@

\Although mountains isolated Yilan by land, the sea provided a way through which indigenous people in Yilan could interact with groups elsewhere, such as indigenous groups, distant traders such as the Han people of China, and Europeans. Large-scale and frequent trading activities brought a wide variety of objects into indigenous communities in Yilan. \The indigenous people of Yilan established their own exchange network that has been described as “inter-insular trade” by @Chen2005 [p. 12] to refer to small-scale regional trade between China and Taiwan on an irregular basis. One of the most commonly traded types of object in this region were personal ornaments such as glass and stone beads. These are one of the most abundant types of foreign goods found at the settlement sites in this region [@Chen2007; @Li2014; @NMTH2005]. Personal adornments in the archaeological record are useful as social signal of an individual's status [@Joyce2005; @Scaramelli2005]. For example, the consumption of stone beads in Southeast Asia during Iron Age is often associated with increasing social stratification or socio-political complexity [@Bellina2014; @Carter2016; @Francis2002; @Theunissen2000; @Kenoyer2000].

@@

# Results of hypothesis testing ?

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
# prepare for JAS:R
# https://www.elsevier.com/journals/journal-of-archaeological-science-reports/2352-409x/guide-for-authors#2000
# not exceed 6000 words excluding figures, tables, highlights 
# iamge Single column	w = 90 mm 
# image Double column w = 190 mm 
```

@@

\Although mountains isolated Yilan by land, the sea provided a way through which indigenous people in Yilan could interact with groups elsewhere, such as indigenous groups, distant traders such as the Han people of China, and Europeans. Large-scale and frequent trading activities brought a wide variety of objects into indigenous communities in Yilan. \The indigenous people of Yilan established their own exchange network that has been described as part of an "inter-insular trade" system [@Chen2005, p. 12] to refer to small-scale regional trade between China and Taiwan on an irregular basis. One of the most commonly traded types of object in this region were personal ornaments such as glass and stone beads. These are one of the most abundant types of foreign goods found at the settlement sites in this region [@Chen2007; @Li2014; @NMTH2005]. Personal adornments in the archaeological record are useful as social signal of an individual's status [@Joyce2005; @Scaramelli2005]. For example, the consumption of stone beads in Southeast Asia during Iron Age is often associated with increasing social stratification or socio-political complexity [@Bellina2014; @Carter2016; @Francis2002; @Theunissen2000; @Kenoyer2000].

@@

# Results of hypothesis testing
